Appendix to "Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2023-07-04 src/docs_paper/appendix.Rmd
Add PC loadings plot to appendix #55

```{r scree, fig.cap="Most variation could be explained by far fewer than the full 24 dimensions."}
knitr::include_graphics("depends/tv-plot.png")
```

```{r reduced-rank, fig.cap="The reduced rank (8) matrix approximation to the Hessian is visually similar to the full rank matrix."}
knitr::include_graphics("depends/reduced-rank-plot.png")
```

>>>>

```{r scree, fig.cap="Most variation could be explained by far fewer than the full 24 dimensions."}
knitr::include_graphics("depends/total-variation.png")
```

```{r pc-loadings, fig.cap="Principal component loadings."}
knitr::include_graphics("depends/pc-loadings.png")
```

```{r reduced-rank, fig.cap="The reduced rank (8) matrix approximation to the Hessian is visually similar to the full rank matrix."}
knitr::include_graphics("depends/reduced-rank.png")
```
